Functional trait data tell new story about biodiversity change

### 2021-02-05 paper/manuscript.Rmd
Methods notes

Biodiversity timeseries were obtained from the Biotime database, a
global repository of assemblage timeseries with 386 individual studies
from multiple taxa. Timeseries were paired with their functional trait
data based on the predominant taxa in the timeseries. Due to limitations
in trait data and processing feasability, we included only mammal, bird,
and amphibian timeseries. Trait data were obtained from Elton Trait
Database (mammals and birds; [@wilman2014]) and Amphibio (amphibians,
[@oliveira2017]).

>>>>

Biodiversity timeseries were obtained from the Biotime database, a
global repository of assemblage timeseries with 386 individual studies
from multiple taxa. Following best practices for the dataset
[@blowes2019] to account for differences in scale between studies, we
aggregated based on a grid system:

*annotation of* `01_biotime_grid.R`

-   label single location (SL) or multiple location (ML), ML with an
    extent less than ((SL extent mean + SL extent SD) are assigned to be
    SL

    -   SL coords are the central lat and long, ML coords are the center
        of convex hull of locations within a rarefyID (grid cell)

-   exclude studies with one year of data

-   create global grid with resolution based on the cutoff study area
    size (SL extent mean + SL extent SD)

-   collate observations for the same study within cells/years

-   remove years (for count) or rarefyID's (for abundance and biomass)
    that do not meet coverage requirement of

Timeseries were paired with their functional trait data based on the
predominant taxa in the timeseries. Due to limitations in trait data and
processing feasability, we included only mammal, bird, and amphibian
timeseries. Trait data were obtained from Elton Trait Database (mammals
and birds; [@wilman2014]) and Amphibio (amphibians, [@oliveira2017]).
